Summary of some simulation results

### 2023-11-28 experiments/tmp-summarize-results.tex
updated readme with simulation setup

% Created 2023-11-21 Tue 15:20
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,danish]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{amsmath}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage[margin=4cm]{geometry}
\usepackage{dsfont, pgfpages, tikz,amssymb, amsmath,xcolor, caption, subcaption}
\input{./latex-settings/standard-settings.tex}
\input{./latex-settings/standard-commands.tex}
\input{./latex-settings/org-settings.tex}
\input{./latex-settings/title-compact.tex}
\author{Anders Munch}
\date{\today}
\title{Summary of some simulation results}
\begin{document}

\maketitle
\section{Super learners}
\label{sec:orgfb13ca2}
In all simulation studies, we compare five super learners, which are listed
below. To evaluate performance super learner, we use an independent data set of
10.000 uncensored samples and calculate the integrated Brier score in this data
set. All results are based on 500 simulated data sets.

@@

\section{Zelefsky based simulation}
\label{sec:org1123149}
We generate data in four different ways:

@@

\subsection{Kaplan-Meier, Cox, and random forest}
\label{sec:org0516d66}
In this setting, we include the following learners in all libraries:

@@

\subsection{Add LASSO}
\label{sec:orgd0d0620}
In this setting we add a learner to all libraries, so that all libraries include
the learners:

@@

\section{Effect of number of variables}
\label{sec:orgf46a6e0}
We generate data in three different way:

@@

\subsection{Kaplan-Meier, Cox, and random forest}
\label{sec:org4b465da}
In this setting, we include the following learners in all libraries:

@@

\subsection{Add LASSO}
\label{sec:org79abb0b}
In this setting we add a learner to all libraries, so that all libraries include
the learners:

@@

\section{References}
\label{sec:org53b63a4}
\renewcommand{\section}[2]{} 
\bibliography{./latex-settings/default-bib.bib}
\end{document}

>>>>

% Created 2023-11-22 Wed 08:53
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,danish]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{amsmath}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage[margin=4cm]{geometry}
\usepackage{dsfont, pgfpages, tikz,amssymb, amsmath,xcolor, caption, subcaption}
\input{./latex-settings/standard-settings.tex}
\input{./latex-settings/standard-commands.tex}
\input{./latex-settings/org-settings.tex}
\input{./latex-settings/title-compact.tex}
\author{Anders Munch}
\date{\today}
\title{Summary of some simulation results}
\begin{document}

\maketitle
\section{Super learners}
\label{sec:org4d4629b}
In all simulation studies, we compare five super learners, which are listed
below. To evaluate performance super learner, we use an independent data set of
10.000 uncensored samples and calculate the integrated Brier score in this data
set. All results are based on 500 simulated data sets.

@@

\section{Zelefsky based simulation}
\label{sec:orgdc8a899}
We generate data in four different ways:

@@

\subsection{Kaplan-Meier, Cox, and random forest}
\label{sec:org3ebe586}
In this setting, we include the following learners in all libraries:

@@

\subsection{Add LASSO}
\label{sec:org98a9507}
In this setting we add a learner to all libraries, so that all libraries include
the learners:

@@

\section{Effect of number of variables}
\label{sec:org2e42afe}
We generate data in three different way:

@@

\subsection{Kaplan-Meier, Cox, and random forest}
\label{sec:org7f2bb4f}
In this setting, we include the following learners in all libraries:

@@

\subsection{Add LASSO}
\label{sec:orgf3d57c9}
In this setting we add a learner to all libraries, so that all libraries include
the learners:

@@

\subsection{Add LASSO and elastic net}
\label{sec:org062c3d9}
In this setting we add a learner to all libraries, so that all libraries include
the learners:

\begin{itemize}
\item The Kaplan-Meier estimator
\item A Cox model with main effects
\item A random forest based on 50 trees
\item A penalized Cox model with main effects, where the \(\|\blank\|_1\) penalty
(LASSO) is used and the penalty parameter is selected using cross-validation
based on Cox' partial likelihood
\item A penalized Cox model with main effects, where the \(\|\blank\|_1 +
  \|\blank\|_2\) penalty (elastic net) is used and the penalty parameter is
selected using cross-validation based on Cox' partial likelihood
\end{itemize}

\begin{figure}[htbp]
\centering
\includegraphics[width=1\linewidth]{/tmp/babel-IUB42s/figure-xTZcFV.pdf}
Zelefsky simulation setting including LASSO into the library
\end{figure}

\section{References}
\label{sec:org3ba31f0}
\renewcommand{\section}[2]{} 
\bibliography{./latex-settings/default-bib.bib}
\end{document}
